Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.tex
Commit 2024-05-23 20:08

>>>>

Created a clear sky approximation and a long term change representation
for a period of 30 years.

Identify CE events and found a trend on \ldots.. The climatology of CE
occurrences over the whole period and the magnitude of the CE events. We
estabished the occurances of extreme CE events \ldots{} The
characteristic of the duration of ``continuous'' CE events. with their
magnitude occurnacies and climatology

Our find have similarities with other mediterranean / europe sites.

The interaction of GHI with the clouds through this period shows a
systematic change.
